The ppmData R-package for setting up spatial point process models

### 2022-12-14 README.Rmd
update to package

```{r,fig.width=6, fig.height=6, fig.cap=""}
pred <- predict(covariates,
                ft.ppm,
                type="response")
plot(pred*prod(res(pred))) # scale response by area of cell.
points(presences[!duplicated(presences),1:2],pch=16,cex=0.75,col=gray(0.2,0.75))

```

>>>>

```{r,fig.width=6, fig.height=6, fig.cap=""}
pred <- predict(covariates,
                ft.ppm,
                type="response")
plot(pred*prod(res(pred))) # scale response by area of cell.
points(presences[!duplicated(presences),1:2],pch=16,cex=0.75,col=gray(0.2,0.75))
```

### Quick comparison of quasirandom quadrature speeds for `ppmData` & `spatstat`

Using `ppmData` to generate a quasi-random scheme
```{r}
system.time(ppmdata2 <- ppmData(npoints = 100000,
                                presences=presences,
                                window = covariates[[1]],
                                covariates=covariates))
```

Using a simple spatstat example to generate a quasi-random scheme
```{r}
suppressPackageStartupMessages(library(spatstat))
data(simdat)
D <- rQuasi(100000,Window(simdat))
system.time(Q <- quadscheme(simdat,D,method="dirichlet", exact=FALSE))
```

### 2022-12-14 paper/paper.Rmd
update to package

The package `spatstat` also allows a user to develop a quasi-random quadrature scheme, but this appears to be quite slow when used with Dirichlet weights for larger numbers of dummy (quadrature) points (\> 10000). For example, a regular window with 100000 quadrature points takes approximately 3.5 minutes to run in `spatstat` using `quadscheme` with `method=Dirichlet`. Our package computes the same Dirichlet tessellation in about 4.5 seconds (Comparisons were from a Linux operating system using a Intel i7 8 core processor, with 16 GB of RAM). Typically, calculating a Dirichlet tessellation increases super-linearly and can become very slow for a large numbers of points. Part of the challenge when developing `ppmData` was to make this step efficient by a C++ implementation of a Delaunay triangulation radial sweep algorithm [@sinclair_s-hull_2016]. The Dirichlet tessellations are then calculated as the dual graph of the Delaunay triangulation. Areal weights for the quadrature points are calculated as the area of each Dirichlet tessellation polygon.

>>>>

The package `spatstat` also allows a user to develop a quasi-random quadrature scheme, but this appears to be quite slow when used with Dirichlet weights for larger numbers of dummy (quadrature) points (\> 10000). For example, a regular window with 100000 quadrature points takes approximately 2.5 minutes to run in `spatstat` using `quadscheme` with `method=Dirichlet` with quasi-random dummy points. Our package computes the same Dirichlet tessellation in about 7.5 seconds (Comparisons were from a Linux operating system using a Intel i7 8 core processor, with 16 GB of RAM, see package readme for a quick comparison). Typically, calculating a Dirichlet tessellation increases super-linearly and can become very slow for a large numbers of points. Part of the challenge when developing `ppmData` was to make this step efficient by a C++ implementation of a Delaunay triangulation radial sweep algorithm [@sinclair_s-hull_2016]. The Dirichlet tessellations are then calculated as the dual graph of the Delaunay triangulation. Areal weights for the quadrature points are calculated as the area of each Dirichlet tessellation polygon.
